**The status of the microbial census: an update**

### 2016-03-14 results/tables/build_bacterial_category_phylum_table.Rmd
Fix residual zoological labels

categories <- c(AE="Aerosol", AQB="Brackish", AQBS="Brackish sediment", AQF="Freshwater", AQFS="Freshwater sediment", AQM="Marine", AQMS="Marine sediment", AQH="Hydrothermal vent", AQI="Ice", AQO="Aquatic other", BD="Digesters", BF="Food-associated", BI="Industrial/mining", BP="Pollution associated", BO="Built other", PR="Plant root", PS="Plant surface", PO="Plant other", SA="Agricultural soil", SD="Desert soil", SP="Permafrost", SO="Other soils", ZV="Vertebrate", ZA="Arthropod", ZN="Other invertebrate", ZO="Other zoological", OT="Other", total="Total")

>>>>

categories <- c(AE="Aerosol", AQB="Brackish", AQBS="Brackish sediment", AQF="Freshwater", AQFS="Freshwater sediment", AQM="Marine", AQMS="Marine sediment", AQH="Hydrothermal vent", AQI="Ice", AQO="Aquatic other", BD="Digesters", BF="Food-associated", BI="Industrial/mining", BP="Pollution associated", BO="Built other", PR="Plant root", PS="Plant surface", PO="Plant other", SA="Agricultural soil", SD="Desert soil", SP="Permafrost", SO="Other soils", ZV="Vertebrate", ZA="Arthropod", ZN="Other invertebrate", ZO="Other host-associated", OT="Other", total="Total")

### 2016-03-14 results/tables/build_coverage_by_category.Rmd
Editing
Fix residual zoological labels

**Table 1. Status of microbial census by habitat classifications and domain.** The isolation_source field from the SILVA reference database was manually curated to assign bacterial and archaeal sequences coarse and fine scale habitat classifications. We calculated the number of sequences and OTUs observed and the percent coverage on a sequence or OTU basis for each classification and domain.

@@

coarse <- c("Aerosol", "Aquatic", "", "", "", "", "", "", "", "", "Built", "", "", "", "", "Plant associated", "", "", "Soil", "", "", "", "Zoological", "", "", "", "Other", "No source data", "Total")

>>>>

**Table 1. Status of microbial census by habitat classifications and domain.** The isolation_source field from the SILVA reference database was manually curated to assign bacterial and archaeal sequences coarse and fine scale habitat classifications. We calculated the number of sequences and OTUs observed and the percent coverage on a sequence or OTU basis for each classification and domain. Descriptions of each category are provided in Table S1.

@@

coarse <- c("Aerosol", "Aquatic", "", "", "", "", "", "", "", "", "Built", "", "", "", "", "Plant associated", "", "", "Soil", "", "", "", "Host-associated", "", "", "", "Other", "No source data", "Total")

### 2016-03-14 results/tables/build_environmental_categories_table.Rmd
Fix residual zoological labels

coarse <- c("\\midrule\\multirow{1}{*}{Aerosol}",
			"\\midrule\\multirow{16}{*}{Aquatic}", "", "", "", "", "", "", "", "",
			"\\midrule\\multirow{10}{*}{Built}", "", "", "", "",
			"\\midrule\\multirow{5}{*}{Plant associated}", "", "",
			"\\midrule\\multirow{6}{*}{Soil}", "", "", "",
			"\\midrule\\multirow{6}{*}{Zoological}", "", "", "",
			"\\midrule\\multirow{1}{*}{Other}")

>>>>

coarse <- c("\\midrule\\multirow{1}{*}{Aerosol}",
			"\\midrule\\multirow{16}{*}{Aquatic}", "", "", "", "", "", "", "", "",
			"\\midrule\\multirow{10}{*}{Built}", "", "", "", "",
			"\\midrule\\multirow{5}{*}{Plant associated}", "", "",
			"\\midrule\\multirow{6}{*}{Soil}", "", "", "",
			"\\midrule\\multirow{6}{*}{Host-associated}", "", "", "",
			"\\midrule\\multirow{1}{*}{Other}")
